---
title: "Plotly Assignment Presentation"
author: "Brian Stewart"
date: "8/18/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
data('mtcars')
```


## Summary

- The following presenation is to help new car buyers understand the effects of Horsepower on car performance, specificly a car's miles per gallon (MPG) rate. 

- Another factor that we will look at is cylinder type as well. This is because horsepower, mpg, and cylinder type are often associated with one another and have great impact on the other two. 

- Hopefully the following graph and analysis can offer some insight into the user's next purchase and allow them to choose the features of a car that mean most to them. 

## Interactive Plot of Horsepower's affect on Miles Per Gallon by Cylinder Type

```{r,echo=FALSE, message=FALSE}

fig <- plot_ly(mtcars, x = ~hp, y = ~mpg, mode = 'markers', color = as.factor(mtcars$cyl), type = 'scatter')
fig <- fig %>% layout(
        title = "Horsepower's affect on Miles Per Gallon by Cylinder Type",
        xaxis = list(title = 'Horsepower'),
        yaxis = list(title = 'Miles Per Gallon'),
        legend = list(title = list(text='<b> Cylinder </b>'))
)

fig
```

## Analysis

- What can be seen from the graph is that there are direct correlations between all three variables chosen in this rudementary analysis.

- ***Horsepower*** and ***cylinder type*** are correlated in the fact that typically the more cylinders in an engine the higher the horsepower. Similarly the higher both ***horsepower*** and ***cylinder type*** the lower the ***MPG*** rate of the car is.

- So there are trade offs for new car buyers. Typically if the buyer is more concerned with efficiency then four cylinder sub 100 horsepower would be the ideal range to look in. On the other hand, if the buyer wants power then an eight cylinder engine with above 200 horse power would be the ideal vehicle. 